Bioverse: Origins of Life

### 2024-07-13 src/tex/ms.tex
Describe hypothesis testing with the Mann-Whitney U test

>>>>

\subsubsection{Hypothesis testing}
To evaluate the evidence for correctly rejecting the null hypothesis, we employed the Mann-Whitney U test~\citep{Mann1947}.
This is a non-parametric test to determine whether two independent samples were drawn from a population with the same distribution and is in particular sensitive to one sample being stochastically greater than the other.
We used the Mann-Whitney U test to compare the distributions of \gls{NUV} fluxes of planets with and without biosignatures.
The implementation in Bioverse relies on the \texttt{scipy.stats.mannwhitneyu} function~\citep{Virtanen2020} and returns a two-tailed p-value, for which we set a significance level of $\alpha = 0.05$ to reject the null hypothesis.
For every hypothesis test, we repeated randomized survey realizations to estimate the fraction of successful rejections of the null hypothesis, i.e., the statistical power of the survey.
